### 2015-12-16 outline.tex
add basic structure and intuition

\vskip.3in
Main idea: adapt SOP model to predict whether anti-dumping measures get renewed
\begin{itemize}
	\item Note that this is not trade war (as far as I know: check with Chad): foreign is applying $\tau^{*a}$ in most / all cases
		\begin{itemize}
			\item When is it worth it for lobby to exert effort to renew AD measure?
		\end{itemize}
\end{itemize}

>>>>

\vskip.3in
Main idea: adapt SOP model to predict whether anti-dumping measures get renewed
\begin{itemize}
	\item Note that this is not trade war: foreign is applying $\tau^{*a}$ in most / all cases
		\begin{itemize}
			\item \textbf{Q}: Are all cases of renewal ones of no punishment, i.e. target country is applying MFN tariff?
		\end{itemize}
	\item When is it worth it for lobby to exert effort to renew AD measure?
	\item Lobby must be able to trigger the AD measure in the first place
		\begin{itemize}
			\item This means disputes/non-adherence to MFN tariffs must happen on the equilibrium path
			\item Need uncertainty, asymmetric information, something
			\item In my model, it is symmetric political uncertainty about how legislators (modeled in reduced form as position of median legislator) will vote
		\end{itemize}
	\item In this setup, need ``dispute'' to last for 5 periods (years)
		\begin{itemize}
			\item Then can extend it.
			\item \textbf{Q}: for five more years?
		\end{itemize}
\end{itemize}
